Overview

### 2021-09-27 overview_gh.Rmd
Update also overview Vig to refect Ying et al.

| function | purpose                                                                                                                                |
|---------:|:---------------------------------------------------------------------------------------------------------------------------------------|
|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test) (Chang et al., 2008)                                         |
|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test) (Chang et al., 2008; aka "T8WSI" in Ying et al. forthcoming) |
| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test)            |
|  `wsi()` | validating a topic model with [word set intrusion test](#word-set-intrusion-test) (Ying et al. forthcoming)                              |
|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard) (see Song et al., 2020)                                              |

@@

Word set intrusion test is a variant of word intrusion test (Ying et al., forthcoming), in which multiple word sets generated from top terms of one topic are juxtaposed with one intruder word set generated similarly from another topic. In Ying et al., this test is called "R4WSI" because 4 word sets are displayed. By default, oolong generates also R4WSI. However, it is also possible to generate R(N)WSI by setting the parameter `n_correct_ws` to N - 1.

@@

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296). [link](https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models)
2. Ying, L., Montgomery, J. M., & Stewart, B. M. (Forthcoming). Inferring concepts from topics: Towards procedures for validating topics as measures. Political Analysis.
3. Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication. [link](https://doi.org/10.1080/10584609.2020.1723752)
4. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
5. Chan et al. (2020) Four best practices for measuring news sentiment using ‘off-the-shelf’ dictionaries: a large-scale p-hacking experiment. Computational Communication Research. [link](https://osf.io/preprints/socarxiv/np5wa/)
6. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903. [link](https://arxiv.org/abs/1103.2903)

>>>>

| function | purpose                                                                                                                           |
|---------:|:----------------------------------------------------------------------------------------------------------------------------------|
|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test) (Chang et al., 2008)                                    |
|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test) (Chang et al., 2008; aka "T8WSI" in Ying et al. 2021) |
| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test)       |
|  `wsi()` | validating a topic model with [word set intrusion test](#word-set-intrusion-test) (Ying et al. 2021)                              |
|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard) (see Song et al., 2020)                                         |

@@

Word set intrusion test is a variant of word intrusion test (Ying et al., 2021), in which multiple word sets generated from top terms of one topic are juxtaposed with one intruder word set generated similarly from another topic. In Ying et al., this test is called "R4WSI" because 4 word sets are displayed. By default, oolong generates also R4WSI. However, it is also possible to generate R(N)WSI by setting the parameter `n_correct_ws` to N - 1.

@@

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296). [link](https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models)
2. Ying, L., Montgomery, J. M., & Stewart, B. M. (2021). Inferring concepts from topics: Towards procedures for validating topics as measures. Political Analysis. [link](https://doi.org/10.1017/pan.2021.33)
3. Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication. [link](https://doi.org/10.1080/10584609.2020.1723752)
4. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
5. Chan et al. (2020) Four best practices for measuring news sentiment using ‘off-the-shelf’ dictionaries: a large-scale p-hacking experiment. Computational Communication Research. [link](https://osf.io/preprints/socarxiv/np5wa/)
6. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903. [link](https://arxiv.org/abs/1103.2903)
